---
title: "Exercises for class 1"
output: html_document
date: "13-02-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rethinking)
```

# Exercises for Class 1

## Supporting code

Below is code from Chapter 2 of the book that you can use to do the exercises. Not all the code you require is here though. Make sure to not rush it and take time to play around with each function. :))

```{r}
# Grid Approximation

# define grid
p_grid = seq(from = 0, to = 1, length.out=20)

# define prior
prior = rep(1, 20)

# compute likelihood at each value in grid
likelihood = dbinom(3, size = 4, prob = p_grid)

likelihood

# compute product of likelihood and prior
unstd.posterior = likelihood * prior

# standardize the posterior so it sums to 1
posterior = unstd.posterior / sum(unstd.posterior)

# plot the distribution
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior_probability")
mtext("20 points")

# we could tabulate this!
table <- data.frame(round(p_grid, 3), round(likelihood, 3), round(posterior, 3))

table

```

```{r}
# Trying to do a Bayesian update:
likelihood = dbinom(3, size = 5, prob = p_grid)

posterior_1 <- posterior

unstd.posterior = likelihood * posterior_1

posterior = unstd.posterior / sum(unstd.posterior)

# plot the distribution
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior_probability")
mtext("20 points")
```


## Exercises

### Easy

2E1. 

```{r}

# (2) p(rain|monday)

# = the probability of rain given that it's monday

```

2E2.

```{r}

# (3)

```

2E3.

```{r}

# (1)

```

2E4.

```{r}

# It means that if you toss the globe for x amount of times, 70% of the time the index finger would land on a water spot.The probability doesn't refer to a concrete count but to a ratio of all trials. This ratio would (in theory?) remain constant as the trial number increases. We could also think of probabilities as an outcome distribution for x amount of trials. The mean of this distribution would in this case be centered around 0.7, with some standard deviation. 

```

### Medium

2M1.

```{r}
# Grid Approximation

# define grid
p_grid = seq(from = 0, to = 1, length.out=20)

plot(p_grid)

# define prior
prior = rep(1, 20)

# compute likelihood at each value in grid
likelihood = dbinom(3, size = 4, prob = p_grid)
likelihood

# compute product of likelihood and prior
unstd.posterior = likelihood * prior

# standardize the posterior so it sums to 1
posterior = unstd.posterior / sum(unstd.posterior)

# plot the distribution
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior_probability")
mtext("20 points")


```



2M2.


```{r}
dbinom(5, size = 7, prob = 0.7)
```


```{r}

dbinom(3, size = 9, prob = 0.5)

```

```{r}

# In the book, McElreath says that we can do much better than choosing a uniform prior for estimating the coverage of water. Is this what we are doing here? How does that impact our estimation?

# That is indeed what we were doing, and the consequence of a uniform prior (a constant of 1), is that the posterior will literally be indentical with the likelihood, since posterior = likelihood * prior

# We assume a new prior that is 0 when p < 0.5, and a positive constant (such as 1) when p > 0.5:

# define grid
p_grid = seq(from = 0, to = 1, length.out=20)

# define prior
prior = c(rep(0, 10), rep(1, 10))

data.frame(p_grid, prior)

# compute likelihood at each value in grid
likelihood = dbinom(3, size = 4, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior = likelihood * prior

# standardize the posterior so it sums to 1
posterior = unstd.posterior / sum(unstd.posterior)

# plot the distribution
plot(p_grid, posterior, type = "b",
     xlab = "probability of water", ylab = "posterior_probability")
mtext("20 points")

```

2M3.

```{r}

# Use the Bayes formula!



```

For the exercises below, I highly suggest you to grab a piece of paper and try to solve the problems in a 'visual' way.

2M4.

```{r}

# Write your probability here.

```

2M5.

```{r}

# Write your probability here.

```

2M6.

```{r}

# Write your probability here.

```
